Distanced-based VOCC analysis

### 2019-06-12 analysis/VOCC/dist-vocc.Rmd
update temperature plots with all biannual-step plots

library(dplyr)
library(ggplot2)
library(sdmTMB)
library(gfranges)
```

@@

nd <- rbind(nd_1, nd_3, nd_4, nd_16)
nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))
```

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) # %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
nd <- nd # %>% filter(ssid == 4)

@@

# can also be filtered to exclude certain years
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)

predictions <- predict(m_temp, newdata = nd)

plot_map <- function(dat, column = "est") {
  ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    facet_wrap(~year) +
    coord_fixed()
}

p <- plot_map(predictions, "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```

Explore subsets ot the spatial range 
```{r eval=FALSE}
predicted1 <- predictions %>% filter(ssid == 1)
predicted3 <- predictions %>% filter(ssid == 3)
predicted4 <- predictions %>% filter(ssid == 4)
predicted16 <- predictions %>% filter(ssid == 16)
predicted1n3 <- predictions %>% filter(ssid != 16) %>% filter(ssid != 4) %>% filter(year > 2004)

p <- plot_map(predicted1n3, "est") +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```

```{r}
out <- make_vector_data(predictions,
  ssid = c(1),
  start_year = 2005,
  input_cell_size = 2,
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_steps = 7,
  indices = c(1, 1, 1, 2, 3, 3, 3),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
glimpse(out)
```

```{r}
gvocc <- plot_vocc(out,
  low_col = "white",
  mid_col = "white",
  high_col = "grey97",
  vec_aes = "distance",
  vec_lwd_range = c(0.5, 0.6),
  max_vec_plotted = 100,
  fill_col = "var_1_s",
  fill_label = "Mean\ntemperature\n2005 & 2007",
  raster_alpha = 1,
  vec_alpha = 0.8
)
gvocc
```

```{r}
gtrend <- plot_vocc(out,
  fill_col = "C_per_decade",
  fill_label = "Temperature\ntrend (°C/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL
)
gtrend
```

```{r}
# png(file = "accasp-wg-fig.png",   # The directory you want to save the file in
# res = 600,
# units = 'in',
# width = 10, # The width of the plot in inches
# height = 7) # The height of the plot in inches

gridExtra::grid.arrange(gtrend, gvocc, nrow = 1)
# dev.off()
```

>>>>

library(dplyr)
library(ggplot2)
library(sdmTMB)
library(gfranges)

```

@@

nd_all <- rbind(nd_1, nd_3, nd_4, nd_16)
nd <- nd_all %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))
```

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) # %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
#nd <- nd_1 # %>% filter(ssid == 4)

@@

# # must be filtered to match years in model
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)

temp <- predict(m_temp, newdata = nd)
```

Define subset of the spatial range 
```{r eval=FALSE}
temperature <- temp %>% 
  # filter(ssid!=3) %>% 
  filter(ssid!=4) %>% 
  filter(ssid!=16) %>% 
  filter(year>2004)

#glimpse(temperature)

temp <-plot_facet_map(temperature, "est", transform_col = no_trans) + 
  labs(fill="kg/ha") +
  ggtitle("Bottom temperature")
print(temp)
```

Biannual changes starting 2005 and ending 2017
```{r}
out1 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2005,
  end_time = 2007,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc1 <- plot_vocc(out1,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2007",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)
#gvocc1 <- gvocc1 + ggtitle("VOCC vectors for <1°C change in bottom temperature")
gvocc1
```

```{r}
out2 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2007,
  end_time = 2009,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc2 <- plot_vocc(out2,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2009",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)

#gvocc2 <- gvocc2 + ggtitle(" ")
gvocc2
```

```{r}
out3 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2009,
  end_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc3 <- plot_vocc(out3,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2011",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)
#gvocc3 <- gvocc3 + ggtitle(" ")
gvocc3
```

```{r}
out4 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2011,
  end_time = 2013,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc4 <- plot_vocc(out4,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2013",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)
#gvocc4 <- gvocc4 + ggtitle(" ")
gvocc4
```

```{r}
out5 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2013,
  end_time = 2015,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc5 <- plot_vocc(out5,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2015",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)
#gvocc5 <- gvocc5 + ggtitle(" ")
gvocc5
```

```{r}
out6 <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2015,
  end_time = 2017,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 2,
  delta_t_step = 2,
  indices = c(1, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
gvocc6 <- plot_vocc(out6,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 50,
  NA_label = ".",
  fill_col = "var_1_e",
  fill_label = "2017",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans,
  raster_limits = c(5, 13)
)
#gvocc6 <- gvocc6 + ggtitle(" ")
gvocc6
```

```{r}
png(file = "biannual_temp_change.png",   # The directory you want to save the file in
res = 600,
units = 'in',
width = 10, # The width of the plot in inches
height = 8) # The height of the plot in inches

gridExtra::grid.arrange(gvocc1, gvocc2, gvocc3, gvocc4, gvocc5, gvocc6, nrow = 2, top = grid::textGrob("VOCC vectors for <0.5°C biannual changes in bottom temperature"))#,gp=gpar(fontsize=20,font=3)) 
dev.off()
```

Cumulative change between last two decades 
VOCC for 0.5 degree change and 1 degree change
```{r}
out0.5d <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2005,
  #skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
```

```{r}
gvocc <- plot_vocc(out0.5,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 100,
  fill_col = "var_1_e",
  fill_label = "2013-2017",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans
)
gvocc <- gvocc + ggtitle("VOCC vectors for <0.5°C change")
gvocc
```

```{r}
out1d <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2005,
  #skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  thresholds = c(1) # vector of plus/minus threshold(s) to define climate match.
)
```

```{r}
gvocc1d <- plot_vocc(out1d,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 100,
  fill_col = "var_1_e",
  fill_label = "2013-2017",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans
)
gvocc1d <- gvocc1d + ggtitle("VOCC vectors for <1°C change")
gvocc1d
```

```{r}
gtrend <- plot_vocc(out1d,
  fill_col = "units_per_decade",
  fill_label = "°C per decade",
  raster_alpha = 1,
  vec_aes = NULL,
  transform_col = no_trans
)
gtrend <- gtrend + ggtitle("Bottom temperature trend 2005-2017")
gtrend
```

```{r}
png(file = "temp-2005-2017-1n3.png",   # The directory you want to save the file in
res = 600,
units = 'in',
width = 10, # The width of the plot in inches
height = 7) # The height of the plot in inches

gridExtra::grid.arrange(gtrend, gvocc, gvocc1d, nrow = 1)
dev.off()
```
